Human capital mediates natural selection in contemporary humans

### 2021-12-30 why-natural-selection.Rmd
Add control for risk attitude to mediation analysis

We are not concerned about endogeneity of polygenic scores, since our theory
requires only that these correlate with human capital. However, endogeneity of
educational attainment is a concern. For example, educational attainment might
correlate with unobserved characteristics that affect one's fertility, e.g. via
success in marriage markets. To partially address this, we include
controls for age, sex, fluid IQ and height in $X$.

>>>>

We are not concerned about endogeneity of polygenic scores, since our theory
requires only that these correlate with human capital. However, endogeneity of
educational attainment is a concern, i.e., educational attainment might
correlate with unobserved characteristics that affect one's fertility (and which
are not related to human capital). To partially address this, we include
controls for age, sex, fluid IQ, height and risk attitude in $X$.
